### 2020-01-23 overview.tex
implemented Luca's comment 1.

Droplets are also important in many artificial and engineering applications.
In material science, technicians can now routinely generate large amount of droplets in massively parallelised microfluidic channels \citep{microfluidics}; these liquid drops can serve as microcontainers, encapsulating functional substances, and subsequently be manipulated and scaffolded into larger stuctures with desired properties (see Figure \ref{fig:photonic-flow}).
In life science, droplet-based microfluidic devices have already been used to automate genome sequencing and, in the future, may enable more effective drug development by building synthetic test platforms more faithful to the human body than the conventional Petri dish \citep{Squires_Quakes_2005, organs-on-chips}.
In transportation, combustion engines rely on the breakup of liquid fuels into tiny drops to enhance mixing, improve combustion efficiency, and reduce pollutant emissions.
And in publications, printed posters, newsletters or books, including this thesis, would not have the same quality without the precise control of pico-litre ($10^{-9}$ mL) ink droplets.

@@

To begin with, recall the incompressible \emph{Navier-Stokes equations}
\begin{subequations} \label{eq:Navier-Sotkes}
 \begin{equation}
   \nabla \cdot {\bm u} = 0,
  \label{eq:div-free}
 \end{equation}
 \begin{equation}
   \rho \bigg(\frac{\partial {\bm u}}{\partial t} + {\bm u} \cdot \nabla {\bm u} \bigg) = -\nabla p + \mu \nabla ^2  {\bm u} + {\bm f},
  \label{eq:NS}
 \end{equation}
\end{subequations}
relating the flow velocity $\bm u$ with the pressure $p$ in the presence of some force density $\bm f$, where $\rho$ and $\mu$ are the density and dynamic viscosity of the fluid, respectively.
Eqs.\ \eqref{eq:Navier-Sotkes}, together with appropriate boundary conditions, govern the dynamics of a Newtonian fluid that satisfies\footnote{The present thesis only concerns Newtonian fluids as the solvent, though, combined with particles, the suspension may exhibit non-Newtonian bulk behaviours. See Section \ref{sec:sus-rheo}.}
\begin{equation}
 \begin{aligned}
   {\bm \sigma} = -p {\bm I}+ \mu \bigg( \nabla {\bm u} + (\nabla {\bm u})^T \bigg),
 \end{aligned}
\end{equation}
where $\bm \sigma$ is the stress tensor, and $\bm I$ the identity matrix.

Depending on the bounding material, conditions on the velocity or stress may be prescribed as boundary conditions. In the case of a solid wall, it is usually the \emph{no-slip} velocity condition; while in the case of a liquid interface, the following stress condition shall be satisfied,
\begin{equation} \label{eq:stress-bc}
  ({\bm \sigma}_+ - {\bm \sigma}_- ) \cdot {\bm n} = \gamma \kappa {\bm n} - \nabla \gamma,
\end{equation}
where $\bm n$ denotes the unit normal vector across the liquid interface (from the $-$ side to the $+$ side), $\gamma$ the surface tension coefficient, and $\kappa$ the curvature of the interface (\eg $\kappa=2/a$ for a sphere of radius $a$).

Eq.\ \eqref{eq:NS} can be further non-dimensionalized, using the reference length $L$, velocity $U$, time $T$, pressure $P \equiv \mu U/L$, and force density $F \equiv P/L$ scales, into
\begin{equation}
   \textrm{Re} \bigg(\textrm{Sr}^{-1} \frac{\partial \hat{\bm u}}{\partial \hat{t}} + \hat{\bm u} \cdot \hat{\nabla} \hat{\bm u} \bigg) =
   -\hat{\nabla} \hat{p} + \hat{\nabla} ^2  \hat{\bm u} + \hat{\bm f},
  \label{eq:NS-nondi}
\end{equation}
where the hat signifies dimensionless quantities, and Re and Sr represent the \emph{Reynolds} and \emph{Strouhal} numbers, defined as
\begin{equation}
  \begin{aligned}
    \textrm{Re} = \frac{\rho UL}{\mu},\quad \quad \textrm{Sr} = \frac{UT}{L}.
  \end{aligned}
\end{equation}
A capillary number can also be defined to non-dimensionalize the surface tension,
\begin{equation}
  \begin{aligned}
    \textrm{Ca} = \frac{\mu U}{\gamma}.
  \end{aligned}
\end{equation}

@@

When both Re and ReSr$^{-1}$ are small, Eq.\ \eqref{eq:NS-nondi} reduces to the \emph{Stokes equation},
\begin{equation}
   -\nabla p + \mu \nabla ^2  {\bm u} + {\bm f} = {\bm 0},
 \label{eq:Stokes}
\end{equation}
or, equivalently
\begin{equation}
   \nabla \cdot  {\bm \sigma} + {\bm f} = {\bm 0},
 \label{eq:Stokes1}
\end{equation}
which we write in the dimensional form.

Physically, the Stokes equation describes systems that are characterised by small length scales or are in slow motions, which are typically encountered in microfluidic or biological applications.
For instance, the Reynolds number based on a 10 $\mu$m droplet traveling at a speed of 10 $\mu$m/s in water ($\rho=10^3$ kg/m$^{3}$, $\mu=10^{-3}$ Pa$\cdot$s) is $10^{-4}$;
and if there is no imposed frequency, the Strouhal number will be 1.
Manifestly, both Re $\ll 1$ and ReSr$^{-1}$ $\ll 1$ are safely satisfied.

@@

\begin{enumerate}
 \item \emph{Linearity}, which makes analytical solutions possible in simple cases and the superposition principle applicable in general. For example, if $({\bm u}_1,p_1)$ is a solution to ${\bm f}={\bm f}_1$ and $({\bm u}_2,p_2)$ is a solution to ${\bm f}={\bm f}_2$, then $(\alpha{\bm u}_1+\beta {\bm u}_2,\alpha p_1 + \beta p_2)$ is a solution to ${\bm f}=\alpha{\bm f}_1 + \beta {\bm f}_2$.
 \item \emph{Reversibility}, or \emph{time reversal symmetry}. This is a consequence of the linearity and entails that, if the forcing changes from ${\bm f}$ to $-{\bm f}$, the flow should reverse, \ie $({\bm u},p) \to (-{\bm u},-p)$. While seemingly redundant, the reversibility symmetry can be very powerful in making \emph{reductio ad absurdum} type-of arguments, see \eg the classical note of \cite{Purcell1977}.
 \item \emph{Stress equilibrium}, which states that any force exerted within the fluid is transmitted instantaneously to the boundary or, if there is no boundary, to infinity \citep{graham_2018}.
 \item \emph{Lorentz reciprocal identity}, which relates two solutions, $({\bm u}', {\bm \sigma}')$ and $({\bm u}'', {\bm \sigma}'')$ (they may differ by boundary conditions), of the Stokes equation by,
 \begin{equation}
  \small
  \begin{aligned}
   \int_V \bigg({\bm u}' \cdot (\nabla  \cdot {\bm \sigma}'') - {\bm u}'' \cdot (\nabla  \cdot {\bm \sigma}')\bigg) dV  & =\\
   \int_S \bigg({\bm u}' \cdot ({\bm \sigma}'' \cdot {\bm n}) - {\bm u}'' \cdot ({\bm \sigma}'  \cdot {\bm n})\bigg) dS, & 
  \end{aligned} \label{eq:lorentz-recip}
 \end{equation}
 where $V$ is some enclosed volume with surface $S$.
 \item \emph{Minimum dissipation principle}. This variational principle asserts that the flow minimizing the energy dissipation rate subject to incompressibility under certain boundary conditions is the Stokes flow under the same boundary conditions.
\end{enumerate}

@@

\bigskip
Imagine the force density ${\bm f}$ in Eq.\ \eqref{eq:Stokes} is singularly supported at the origin, \ie ${\bm f}({\bm x})={\bm F}\delta({\bm x})$, $\delta$ being the Dirac delta. This might represent a reasonable approximation of a small sedimenting particle viewed from a distance. Then, the solution of the Stokes equation due to this forcing can be written as
\begin{equation} \label{eq:stokes-green}
 \begin{aligned}
   {\bm u}({\bm x}) = {\bm G}({\bm x}) \cdot {\bm F},
 \end{aligned}
\end{equation}
where  
\begin{equation} \label{eq:stokeslet}
 \begin{aligned}
   {\bm G}({\bm x}) = \frac{1}{8\pi\mu } \bigg( \frac{{\bm I}}{\abs{\bm x}}+\frac{ {\bm x}{\bm x} }{ \abs{{\bm x}}^3 } \bigg),
 \end{aligned}
\end{equation}
is the free-space Green's function, also known as the \emph{Stokeslet} or \emph{Oseen tensor}.

@@

Eq.\ \eqref{eq:multipole} is the \emph{multipole expansion} of the disturbance velocity, ${\bm u}-{\bm u}^\infty$. One immediate physical implication is that a forced particle (\eg a rising bubble) will generate a disturbance that decays as $1/\abs{\bm x}$, while a force-free particle (\eg a self-propelled bacterium) has a $1/\abs{\bm x}^2$ decay thus leaving less trace at the same distance away. See Figure \ref{fig:lets} for illustrations.\footnote{The rotlet flow is simply a rigid-body rotation centered at the origin.}

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.49\columnwidth]{stokeslet1.pdf}
  \includegraphics[width=0.49\columnwidth]{stresslet1.pdf}
  \caption{Flow fields due a Stokeslet (left) and a stresslet (right) centered at the origin (red dot). The black arrows display the velocities, while their directions are also indicated by the gray arrows. The flow fields are both axi- and fore-aft symmetric. Note the difference in the velocity magnitude of the two flows.}
  \label{fig:lets}
\end{figure}

@@

The preceding section presents the most basic solutions of the Stokes equation in the presence of one particle.
In practice, however, it is rarely the case particles or droplets exist in isolation.
Particles tend to abound; and they often interact with each other through various types of hydrodynamic or non-hydrodynamic mechanisms, giving rise to a multitude of phenomena in natural or artificial conditions.
For example, soap bubbles are always in a cluster due to the interfacial capillary attraction, while the same underlying principle can be applied to manipulate droplet motions on a surface to aid liquid handling \citep{vapour-sensing}.
To offer at least some partial insights on the hydrodynamics, we highlight recent theoretical developments of droplet interactions in bulk microflows, starting from the simplest case of two particles immersed in unbounded simple shear flows.

@@

\cite{Zinchenko1983,Zinchenko1984} considered the problem when the two particles are ``fluid spheres''.
Specifically, he calculated the scalar parameters introduced in \cite{batchelor_green_1972} for two identical droplets, and showed that they are functions of the relative position and viscosity ratio, $\lambda$, defined as the ratio between the droplet and the solvent viscosities.
For $\lambda=$ 0.25 to 20, the phase diagram  in simple shear flows has similar topological features to the case of rigid particles,\footnote{Different types of trajectories were also hypothesized, which may only exist in the case of liquid drops. See \cite{Zinchenko1984} for details.} \ie an open region and a closed region, though its asymptotic limit depends on the viscosity ratio and short-range non-hydrodynamic interactions, cf.\ the DLVO theory.

For the above analysis to hold for liquid droplets, an additional constraint must be satisfied, \ie Ca $\ll 1$.
This is usually the case for microfluidic applications. For instance, recall the case considered in the beginning of Section \ref{sec:stokes-flows}, and suppose it is an oil droplet traveling in water under a relatively large local shear rate of $\dot{\gamma}=10^3$ s$^{-1}$. The surface tension coefficient would be around 0.05 N/m, depending on surfactants and the temperature, resulting in Ca $=\mu(a\dot{\gamma})/\gamma \sim 10^{-4}$. Clearly, the capillary number is small enough for the droplet to remain spherical in the flow.

@@

When particles are at close contact, say the surface gap $h \ll a$, with $a$ being the particle radius. Then, the hydrodynamic interaction will be dominated by the lubrication term. Specifically, the lubrication force diverge as $a/h$ in the longitudinal direction, and as $\log(a/h)$ in the transverse directions \citep{jeffrey_onishi_1984, jeffrey1992}. Qualitatively, lubrication functions as a dashpot that prevents incoming particles from colliding and separating particles from overshooting. These will be further discussed and demonstrated in Section \ref{sec:num-dem} and \emph{Papers 7 \& 8}.

@@

Beginning with the simplest case where only one wall is remotely present, \cite{Fouxon_Rubinstein2019} recently derived the relative velocity of two rigid particles as a sum of the BG's velocity and a wall-correction term (\emph{Paper 4}). The solution is constructed from an boundary integral representation of channel flows using multipole expansions similar to Eq.\ \eqref{eq:multipole}, see \cite{Fouxon_2017} (\emph{Paper 3}) for details.
Figure \ref{fig:itzhak-boris} illustrates the main results.
Here, the lines depicts the relative trajectories of the second particle in the shear plane, where the velocity is in the $x$ direction and increases with $z$. The wall is located at $z=-z_0$.
Remarkably, there exist two types of closed trajectories (in blue) and two types of open trajectories (in red).
Close to the origin, a degenerate of the BG-type closed trajectory is singly connected to an open trajectory at an unstable saddle point at distance $r_s$ from the origin.
The latter is not admissible in BG, as the particles swap their $z$ coordinates after a binary encounter rather than returning to the original positions.
Such open trajectories have been previously termed ``swapping trajectories'' and recognized as a wall-induced cross-streamline particle migration mechanism, attributing to the anomalously large self-diffusivity observed in a dilute suspension measurement \citep{Zarraga_Leighton2002, zurita-gotor_2007}.
Our derivation and numerical simulations independently verify this result.

@@

Extending further away from the reference particle, we identify a new class of closed trajectories along which the second particle rotates around a neural equilibrium center. Note that, despite a distant wall, the trajectories remain axisymmetric with respect to the $x$ axis. Thus, all points on the circle $x^2+y^2=r_c^2$ are stationary configurations.
Slightly moving away from the center point, the second particles will revolve perpetually as it is convected by the flow; hence, we call them the ``dancing trajectories'' (see Figure \ref{fig:itzhak-boris}, right).
The positions of these critical points are approximately related to the wall separation alone. Specifically, $r_s=(32z_0^3/15)^{1/5}$ and $r_c \approx 4z_0$.
Overall, the wall is a singular perturbation to the free-space particle interaction.

@@

Secondly, the effect of a rigid boundary on particle interactions can sometimes be intuitively predicted by image analyses utilizing basic solutions of the Stokes equation.
For example, \cite{zurita-gotor_2007} performed a relatively simple analysis to explain the flow reversal pattern (\ie the swapping trajectories) by calculating the scattering flow.
As sketched in Figure \ref{fig:stresslet-refl}, the wall reflection of the stresslet flow (since the particles are force-free) produces a vertical velocity component consistent with what is required for the position swapping (see \cite{zurita-gotor_2007} for the detailed calculations). This flow, despite being very small, is what causes the second particle to be shielded from the first one.

Thirdly, we note that these observed particle interactions may be superimposed pairwise to infer the collective dynamics of a group of particles in similar conditions.
To illustrate this point, we simulated two rigid particles in a periodic channel (thus mimicking a 1D crystal) and observed a crossover from permanent separation of the particle pair (for $0.32 \lessapprox z_0/H \lessapprox 0.68$) to a trapping state (for $z_0/H \lessapprox 0.32$ or $z_0/H \gtrapprox 0.68$), where $H$ is the channel height (same setup and notation otherwise, cf.\ Figures \ref{fig:itzhak-boris} and \ref{fig:stresslet-refl}).
Qualitatively, the former results from cross-stream migrations that resemble the BG open trajectories, while the latter is due to position swappings with neighbouring particles strongly influenced by the wall.
See \cite{Beatus2006, Janssen2012, Uspal2013} for a few more analogous and vivid demonstrations.

@@

The last two decades has witnessed a boom of studies on hydrodynamic interactions in strongly confined geometries owing to the development of microfluidics \citep{Cui_etal_2002, Cui2004, tlusty, Davit_2008, q2d_Beatus}. At a first glance, increasing the confinement seems to complicate the problem as the boundary conditions becomes non-negligible (as opposed to being infinitely away), see \eg \cite{LironMochon, Fouxon_Rubinstein2019}. However, by returning to the physical origin of the equations, one can surprisingly gain a useful insight applicable to a wide range of geometries and particle sizes \citep{Diamant_2005}. Below, we exemplify two such conditions, one in which the interacting droplets are confined between two rigid planes, the other between free surfaces. The solutions are simplified by focusing on the far-field interactions and realizing that the problem is \emph{quasi-two-dimensional} (q2D).

@@

Under such conditions, the velocity field is irrotational and satisfies the boundary conditions of zero normal components at a rigid boundary in the horizontal plane \citep{Batchelor}. That is, a moving droplet (shaped as a pancake in q2D) shall have zero mass flux through its edge, not no-slip. With these requirements, it can be shown that the flow, created by the drop far from its surface, is proportional to
%Similar to the derivation for the Stokeslet, the flow ${\bm u}$ due to a moving droplet can be approxmiately derived, which has the following far-field structure
\begin{equation} \label{eq:dipolar}
 \begin{aligned}
   {\bm B}^s({\bm x}) \approx -\frac{\alpha H}{\mu} \bigg( \frac{{\bm I}}{\abs{\bm x}^2} -\frac{ 2{\bm x}{\bm x} }{ \abs{{\bm x}}^4} \bigg),
   \quad \textrm{for} \quad \abs{\bm x} \gg H,
 \end{aligned}
\end{equation}
where $\alpha$ is a dimensionless prefactor depending on the confinement \citep{Diamant}.

Physically, the above equation describes a 2D \emph{mass dipole} that displaces the surrounding fluid as the droplet moves.
Mathematically, it is the q2D Oseen tensor that approximates the velocity due to forcing on a moving droplet from afar, \ie ${\bm u} \sim {\bm B}{\bm F}$.
Specifically, ${\bm u}$ decays with the distance as $1/\abs{\bm x}^2$, which is faster than the free-space Stokeslet flow, but surprisingly slower than the flow caused by a moving particle near a single plate \citep{Cui2004}.
Heuristic arguments based on conservation laws have been proposed to explain these scaling differences, see \cite{Diamant} for details.

@@

>>>>

Droplets are also important in many artificial and engineering applications.
In material science, technicians can now routinely generate large amount of droplets in massively parallelised microfluidic channels \citep{microfluidics}; these liquid drops can serve as microcontainers, encapsulating functional substances, and subsequently be manipulated and scaffolded into larger stuctures with desired properties.
In life science, droplet-based microfluidic devices have already been used to automate genome sequencing and, in the future, may enable more effective drug development by building synthetic test platforms more faithful to the human body than the conventional Petri dish \citep{Squires_Quakes_2005, organs-on-chips}.
In transportation, combustion engines rely on the breakup of liquid fuels into tiny drops to enhance mixing, improve combustion efficiency, and reduce pollutant emissions.
Even in publications, printed posters, newsletters or books, including this thesis, would not have the same quality without the precise control of pico-litre ($10^{-9}$ mL) ink droplets.

@@

To begin with, recall the incompressible \emph{Navier-Stokes equations}
\begin{subequations} \label{eq:Navier-Sotkes}
 \begin{equation}
   \nabla \cdot {\bm u} = 0,
  \label{eq:div-free}
 \end{equation}
 \begin{equation}
   \rho \bigg(\frac{\partial {\bm u}}{\partial t} + {\bm u} \cdot \nabla {\bm u} \bigg) = -\nabla p + \mu \nabla ^2  {\bm u} + {\bm f},
  \label{eq:NS}
 \end{equation}
\end{subequations}
relating the flow velocity $\bm u$ with the pressure $p$ in the presence of some force density $\bm f$, where $\rho$ and $\mu$ are the density and dynamic viscosity of the fluid.
Eqs.\ \eqref{eq:Navier-Sotkes}, together with appropriate boundary conditions, govern the dynamics of a Newtonian fluid that satisfies\footnote{The present thesis only concerns Newtonian fluids as the solvent, though, combined with particles, the suspension may exhibit non-Newtonian bulk behaviours. See Section \ref{sec:sus-rheo}.}
\begin{equation}
 \begin{aligned}
   {\bm \sigma} = -p {\bm I}+ \mu \bigg( \nabla {\bm u} + (\nabla {\bm u})^T \bigg),
 \end{aligned}
\end{equation}
where $\bm \sigma$ is the stress tensor, and $\bm I$ the identity matrix.

Depending on the bounding material, conditions on the velocity or stress may be prescribed as boundary conditions. In the case of a solid wall, it is usually the \emph{no-slip} velocity condition; while in the case of a liquid interface, the following stress condition shall be satisfied,
\begin{equation} \label{eq:stress-bc}
  ({\bm \sigma}_+ - {\bm \sigma}_- ) \cdot {\bm n} = \gamma \kappa {\bm n} - \nabla \gamma,
\end{equation}
where $\bm n$ denotes the unit normal vector across the liquid interface (from the $-$ side to the $+$ side), $\gamma$ the surface tension coefficient, and $\kappa$ the curvature of the interface (\eg $\kappa=2/a$ for a sphere of radius $a$).
The above equation states that both normal and tangential stresses can be discontinuous across an interface.

Eq.\ \eqref{eq:NS} can be further non-dimensionalized, using the reference length $L$, velocity $U$, time $T$, pressure $P \equiv \mu U/L$, and force density $F \equiv P/L$ scales, into
\begin{equation}
   \textrm{Re} \bigg(\textrm{Sr}^{-1} \frac{\partial \hat{\bm u}}{\partial \hat{t}} + \hat{\bm u} \cdot \hat{\nabla} \hat{\bm u} \bigg) =
   -\hat{\nabla} \hat{p} + \hat{\nabla} ^2  \hat{\bm u} + \hat{\bm f},
  \label{eq:NS-nondi}
\end{equation}
where the hat signifies dimensionless quantities, and Re and Sr represent the \emph{Reynolds} and \emph{Strouhal} numbers, defined as
\begin{equation}
  \begin{aligned}
    \textrm{Re} = \frac{\rho UL}{\mu},\quad \quad \textrm{Sr} = \frac{UT}{L}.
  \end{aligned}
\end{equation}
A capillary number can also be defined to non-dimensionalize the surface tension appearing in Eq.\ \eqref{eq:stress-bc},
\begin{equation}
  \begin{aligned}
    \textrm{Ca} = \frac{\mu U}{\gamma}.
  \end{aligned}
\end{equation}

@@

When both Re and ReSr$^{-1}$ are small, Eq.\ \eqref{eq:NS-nondi} reduces to the \emph{Stokes equation},
\begin{equation}
   -\nabla p + \mu \nabla ^2  {\bm u} + {\bm f} = {\bm 0},
 \label{eq:Stokes}
\end{equation}
or, equivalently
\begin{equation}
   \nabla \cdot  {\bm \sigma} + {\bm f} = {\bm 0}.
 \label{eq:Stokes1}
\end{equation}
%which we write in the dimensional form.

Physically, the Stokes equation describes systems that are characterised by small length scales or are in slow motions, which are typically encountered in microfluidic or biological applications.
For instance, the Reynolds number based on a 10 $\mu$m droplet traveling at a speed of 10 $\mu$m/s in water ($\rho=10^3$ kg/m$^{3}$, $\mu=10^{-3}$ Pa$\cdot$s) is $10^{-4}$;
and if there is no imposed frequency, the Strouhal number will be 1.
Manifestly, both Re $\ll 1$ and ReSr$^{-1}$ $\ll 1$.

@@

\begin{enumerate}
 \item \emph{Linearity}, which makes analytical solutions possible in simple cases and the superposition principle applicable in general. For example, if $({\bm u}_1,p_1)$ is a solution to ${\bm f}={\bm f}_1$ and $({\bm u}_2,p_2)$ is a solution to ${\bm f}={\bm f}_2$, then $(\alpha{\bm u}_1+\beta {\bm u}_2,\alpha p_1 + \beta p_2)$ is a solution to ${\bm f}=\alpha{\bm f}_1 + \beta {\bm f}_2$.
 \item \emph{Reversibility}, or \emph{time reversal symmetry}. This is a consequence of the linearity and entails that, if the forcing changes from ${\bm f}$ to $-{\bm f}$, the flow should reverse, \ie $({\bm u},p) \to (-{\bm u},-p)$. While seemingly redundant, the reversibility symmetry can be very powerful in making \emph{reductio ad absurdum} type-of arguments, see \eg the classical note of \cite{Purcell1977}.
 \item \emph{Stress equilibrium}, which states that any force exerted within the fluid is transmitted instantaneously to the boundary or, if there is no boundary, to infinity \citep{graham_2018}.
 \item \emph{Lorentz reciprocal identity}, which relates two solutions, $({\bm u}', {\bm \sigma}')$ and $({\bm u}'', {\bm \sigma}'')$ (they may differ by boundary conditions), of the Stokes equation by,
 \begin{equation}
  \small
  \begin{aligned}
   \int_V \bigg({\bm u}' \cdot (\nabla  \cdot {\bm \sigma}'') - {\bm u}'' \cdot (\nabla  \cdot {\bm \sigma}')\bigg) dV  & =\\
   \int_S \bigg({\bm u}' \cdot ({\bm \sigma}'' \cdot {\bm n}) - {\bm u}'' \cdot ({\bm \sigma}'  \cdot {\bm n})\bigg) dS, & 
  \end{aligned} \label{eq:lorentz-recip}
 \end{equation}
 where $V$ is some enclosed volume with surface $S$. This identity is often useful in analytical calculations.
 \item \emph{Minimum dissipation principle}. This variational principle asserts that the flow minimizing the energy dissipation rate subject to incompressibility under certain boundary conditions is the Stokes flow under the same boundary conditions. Turbulent flow, on the contrary, is very dissipative.
\end{enumerate}

@@

\medskip
Imagine the force density ${\bm f}$ in Eq.\ \eqref{eq:Stokes} is singularly supported at the origin, \ie ${\bm f}({\bm x})={\bm F}\delta({\bm x})$, $\delta$ being the Dirac delta.
This might represent a reasonable approximation of a small sedimenting particle viewed from a large distance.
Then, the solution of the Stokes equation due to this forcing can be written as
\begin{equation} \label{eq:stokes-green}
 \begin{aligned}
   {\bm u}({\bm x}) = {\bm G}({\bm x}) \cdot {\bm F},
 \end{aligned}
\end{equation}
where  
\begin{equation} \label{eq:stokeslet}
 \begin{aligned}
   {\bm G}({\bm x}) = \frac{1}{8\pi\mu } \bigg( \frac{{\bm I}}{\abs{\bm x}}+\frac{ {\bm x}{\bm x} }{ \abs{{\bm x}}^3 } \bigg),
 \end{aligned}
\end{equation}
is the free-space Green's function, also known as the \emph{Stokeslet} or \emph{Oseen tensor}.

@@

Eq.\ \eqref{eq:multipole} is the \emph{multipole expansion} of the disturbance velocity, ${\bm u}-{\bm u}^\infty$. One immediate physical implication is that a forced particle (\eg a rising bubble) will generate a disturbance that decays as $1/\abs{\bm x}$, while a force-free particle (\eg a self-propelled bacterium) has a $1/\abs{\bm x}^2$ decay thus leaving less trace at the same distance. See Figure \ref{fig:lets} for illustrations.\footnote{The rotlet flow is simply a rigid-body rotation centered at the origin.}

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.49\columnwidth]{stokeslet1.pdf}
  \includegraphics[width=0.49\columnwidth]{stresslet1.pdf}
  \caption{Flow fields due a Stokeslet (left) and a stresslet (right) centered at the origin (red dot). The black arrows display the velocity magnitude, while their directions are also indicated by the gray arrows. The flow fields are both axi- and fore-aft symmetric. Note the difference in the velocity magnitude of the two flows.}
  \label{fig:lets}
\end{figure}

@@

The preceding section presents the most basic solutions of the Stokes equation in the presence of one particle.
In practice, however, it is rarely the case particles or droplets exist in isolation.
Particles tend to abound; and they often interact with each other through various types of hydrodynamic or non-hydrodynamic mechanisms, giving rise to a multitude of phenomena in natural or engineering applications.
For example, soap bubbles are always in a cluster due to the interfacial capillary attraction, while the same underlying principle can be applied to manipulate droplet motions on a surface to aid liquid handling \citep{vapour-sensing}.
To offer at least some partial insights on the hydrodynamics, we highlight recent theoretical developments of droplet interactions in bulk microflows, starting from the simplest case of two particles immersed in unbounded simple shear flows.

@@

\cite{Zinchenko1983,Zinchenko1984} considered the problem when the two particles are ``fluid spheres''.
Specifically, he calculated the scalar parameters introduced in \cite{batchelor_green_1972} for two identical droplets, and showed that they are functions of the relative position and viscosity ratio, $\lambda$, defined as the ratio between the droplet and the solvent viscosities.
For $\lambda=$ 0.25 to 20, the phase diagram in simple shear flows has similar topological features to the case of rigid particles,%
\footnote{Different types of trajectories were also hypothesized, which may only exist in the case of liquid drops. See \cite{Zinchenko1984} for details.}
\ie an open region and a closed region, though its asymptotic limit depends on the viscosity ratio and short-range non-hydrodynamic interactions.%
\footnote{In the original work of Zinchenko, he used the DLVO theory, which includes the van der Waals attraction and the electrostatic repulsion, for droplets in close contact. Other type of forces, such as the depletion attraction (cf.\ \emph{Papers 1 \& 2}), are also possible and may lead to different pair interactions.}

For the above analysis to hold for liquid droplets, an additional constraint must be introduced, \ie Ca $\ll 1$.
This is usually the case for microfluidic applications. For instance, recall the case considered in the beginning of Section \ref{sec:stokes-flows}, and suppose it is an oil droplet traveling in water under a relatively large local shear rate of $\dot{\gamma}=10^3$ s$^{-1}$. The surface tension coefficient would be around 0.05 N/m, depending on surfactants and the temperature, resulting in Ca $=\mu(a\dot{\gamma})/\gamma \sim 10^{-4}$. Clearly, the capillary number is small enough for the droplet to remain spherical in the flow.

@@

When particles are at close contact, say the surface gap $h \ll a$, with $a$ being the particle radius. Then, the hydrodynamic interaction will be dominated by the lubrication term. Specifically, the lubrication force diverge as $a/h$ in the longitudinal direction, and as $\log(a/h)$ in the transverse directions \citep{jeffrey_onishi_1984, jeffrey1992}. Qualitatively, lubrication functions as a dashpot that prevents incoming particles from colliding and separating particles from overshooting. These will be further discussed and demonstrated in Section \ref{sec:num-dem} and \emph{Paper 7}.

@@

Beginning with the simplest case where only one wall is remotely present, \cite{Fouxon_Rubinstein2019} recently derived the relative velocity of two rigid particles as a sum of the BG's velocity and a wall-correction term (\emph{Paper 4}). The solution is constructed from an boundary integral representation of channel flows using multipole expansions similar to Eq.\ \eqref{eq:multipole}, see \cite{Fouxon_2017} (\emph{Paper 3}) for details.
Figure \ref{fig:itzhak-boris} illustrates the main results.
Here, the lines depicts the relative trajectories of the second particle in the shear plane, where the velocity is in the $x$ direction and increases with $z$. The wall is located at $z=-z_0$.
Remarkably, there exist two types of closed trajectories (in blue) and two types of open trajectories (in red).
Close to the origin, a degenerate of the BG-type closed trajectory is singly connected to an open trajectory at an unstable saddle point at distance $r_s$ from the origin.
The latter is not admissible in BG, as the particles swap their $z$ coordinates after a binary encounter rather than returning to the original positions.
Such open trajectories have been previously termed ``swapping trajectories'' and recognized as a wall-induced cross-streamline particle migration mechanism, explaining the anomalously large self-diffusivity observed in a dilute suspension measurement \citep{Zarraga_Leighton2002, zurita-gotor_2007}.
Our derivation and numerical simulations independently verify this result.

@@

Extending further away from the reference particle, we identify a new class of closed trajectories along which the second particle rotates around a neutral equilibrium center. Note that, despite a distant wall, the trajectories remain axisymmetric with respect to the $z$ axis. Thus, all points on the circle $x^2+y^2=r_c^2$ are stationary configurations.
Slightly moving away from the center point, the second particles will revolve perpetually as it is convected by the flow; hence, we call them the ``dancing trajectories'' (see Figure \ref{fig:itzhak-boris}, right).
The positions of these critical points are approximately related to the wall separation alone. Specifically, $r_s=(32z_0^3/15)^{1/5}$ and $r_c \approx 4z_0$.
Overall, the wall is a singular perturbation to the free-space particle interaction.

@@

Secondly, the effect of a rigid boundary on particle interactions can sometimes be intuitively predicted by image analyses utilising basic solutions of the Stokes equation.
For example, \cite{zurita-gotor_2007} performed a relatively simple analysis to explain the flow reversal pattern (\ie the swapping trajectories) by calculating the scattering flow.
As sketched in Figure \ref{fig:stresslet-refl}, the wall reflection of the stresslet flow (the particles are force-free) produces a vertical velocity component consistent with what is required for the position swapping (see \cite{zurita-gotor_2007} for the detailed calculations). This flow, despite being very small, is what causes the second particle to be shielded from the first one.

Thirdly, we note that these observed particle interactions may be superimposed pairwise to infer the collective dynamics of a group of particles in similar conditions.
To illustrate this point, we simulated two rigid particles in a periodic channel (thus mimicking a 1D crystal) and
observed a crossover from permanent separation of the particle pair (for $0.32 \lessapprox z_0/H \lessapprox 0.68$)
to a trapping state (for $z_0/H \lessapprox 0.32$ or $z_0/H \gtrapprox 0.68$),
where $H$ is the channel height;%
\footnote{The computational setup and notations are the same as the case presented before, cf.\ Figures \ref{fig:itzhak-boris} and \ref{fig:stresslet-refl}.}
see Figure \ref{fig:xover}.
Qualitatively, the former results from cross-stream migrations that resemble the BG open trajectories,
while the latter is due to position swappings with neighbouring particles strongly influenced by the wall.
See \cite{Beatus2006, Janssen2012, Uspal2013} for a few more analogous and vivid demonstrations.

@@

The last two decades has witnessed a boom of studies on hydrodynamic interactions in strongly confined geometries owing to the development of microfluidics \citep{Cui_etal_2002, Cui2004, tlusty, Davit_2008, q2d_Beatus}.
At a first glance, increasing the confinement seems to complicate the problem as the boundary effects become less negligible, see \eg \cite{LironMochon, Fouxon_Rubinstein2019}.
However, by returning to the physical origin of the equations, one can surprisingly gain a useful insight applicable to a wide range of geometries and particle sizes \citep{Diamant_2005}. Below, we exemplify two such conditions, one in which the interacting droplets are confined between two rigid planes, the other between free surfaces. The solutions are simplified by focusing on the far-field interactions and realizing that the problem is \emph{quasi-two-dimensional} (q2D).

@@

Under such conditions, the velocity field is irrotational and satisfies the boundary conditions of zero normal components at a rigid boundary in the horizontal plane \citep{Batchelor}.
That is, a moving droplet (shaped as a pancake in q2D) shall have zero mass flux through its edge, not no-slip.
With these requirements, it can be shown that the flow created by the drop far from its surface is proportional to
\begin{equation} \label{eq:dipolar}
 \begin{aligned}
   {\bm B}^s({\bm x}) \approx -\frac{\alpha H}{\mu} \bigg( \frac{{\bm I}}{\abs{\bm x}^2} -\frac{ 2{\bm x}{\bm x} }{ \abs{{\bm x}}^4} \bigg),
   \quad \textrm{for} \quad \abs{\bm x} \gg H,
 \end{aligned}
\end{equation}
where $\alpha$ is a dimensionless prefactor depending on the confinement \citep{Diamant}.

Physically, the above equation describes a 2D \emph{mass dipole} that displaces the surrounding fluid as the droplet moves.
Mathematically, it is the q2D Oseen tensor that approximates the far-field velocity due to forcing on a moving droplet, \ie ${\bm u} \sim {\bm B}{\bm F}$.
Specifically, ${\bm u}$ decays with the distance as $1/\abs{\bm x}^2$, which is faster than the free-space Stokeslet flow, but surprisingly slower than the flow caused by a moving particle near a single plate \citep{Cui2004}.
Heuristic arguments based on conservation laws have been proposed to explain these scaling differences, see \cite{Diamant} for details.

@@

%%%%%%% ------------- IMPROVE THIS SECTION ---------------- %%%%%%%%%%
